On the eletrodynamic of moving bodies

### 2019-05-29 Article_AS.Rmd
MM

## Sampling
The dataset used in this study came from genetic selection for a series of tests according to provenances [@Beaulieu1996]. The improvement program for this region was led by Quebec’s Ministry of Forests, Wildlife and Parcs, Canada. Experimental plantings were initiated from white spruce seedlings grown in nurseries and planted at two years of age at a regular spacing between trees of 2 m in all directions. This series of tests was established in 1999 by the Canadian Forest Service and is one of the three essential parts of the white spruce breeding program in Quebec. Two sites were selected for sampling: one near Saint-Casimir, Quebec (46.6994, -72.1119), in the maple–basswood ecological zone (warm weather) , and the other one near Cabano (Asselin), Quebec (47.8808, -68.4436), in the balsam fir-yellow birch ecological zone (cool weather). Between nine and 14 trees per site were sampled from each of the 93 full-sib families, for a total sample of 2365 trees (fig 1). Trees were 15 years old at the time of sampling. Trees were assigned to row-plots of five trees/plot (2 m × 2 m spacing). Core samples were extracted at breast height (1.3 m above ground level) from the southern side of the trees to minimize the variation due to sample orientation. Tree height and diameter at breast height (DBH, 1.3 m above ground) were recorded in 2015 at the age of 15 years, and a wood increment core was extracted from the south facing side of each tree. Cores were stored in a freezer, conditioned to 7% moisture and cut to 1.68 mm thickness prior to X-ray densitometry analyses (Quintek Measurement Systems, TN). Wood density was calculated as a ring area weighted mean from recorded pith to bark wood density profiles.

@@

where RD is the mean ring density (kgm-3), CA is cambial age (years), $b_0$, $b_1$ and $b_2$ are empirically determined parameters, and e is the residual error term. Parameter $b_0$ denotes the intercept when CA approaches a theoretical value of 0. We noticed that it was impossible to optimize the equation using the same estimated parameters for all tree cores, because the pattern of variation of annual rings average density of each tree is more or less different from the others. We, therefore, used the optim function of the stats package in the R [@R2018] statistical programming environment to find the best parameters iteratively for each tree core . The fit of the model was evaluated by visual analysis of the model residual curves against adjusted values and explanatory variables, fit indices (R2) [@Pape1999]. The graphic description in figure 1 of the three parameters of our model makes it possible to understand how each parameter influences our model (Fig 2).

@@

It can be observed in figure 1 that the parameters $b_0$ and $b_1$ influence the whole of the curve. An increase of one of these parameters leads to that of the density on all rings. Unlike parameter $b_0$ and $b_1$, parameter $b_2$ seems to be influenced by some of the density. A low value of this parameter causes a sharp increase of the density starting from the third ring and when this parameter increases a decrease of the density is observed at this level until the curve is similar to the cases of the parameters $b_0$ and $b_1$. Beyond the value 1, the parameter $b_2$ does not influence the variation of the density.\

## Determination of the wood density uniformity index
The uniformity index is an index to determine the variation in the density of pith-to-bark in order to identify tree families that are least sensitive to variations in climatic conditions. The residues of our model were used to obtain the wood density uniformity index, which was determined using an equation. We subtracted the density residues values of year $n-1$ from year $n$. We were interested more specifically in the difference between the average density residues of annual rings of two consecutive years, no matter whether the difference was positive or negative. The absolute value was used for each difference to get rid of the sign. The index was estimated from the following formula:

$$H = \sum | D_n - D_{n - 1} |$$

Where H is the uniformity index, $D_n$ is the wood density residues of year $N$ and  $D_n - 1$ is the tree density residues of year $N-1$.

## Spearman’s rank correlation coefficient (Spearman’s rho) 
To describe the link between two variables by means of a monotonic function, we used Spearman’s rank correlation coefficient. We calculated this coefficient for the index of uniformity and the different parameters of the model. The elements for which we calculated Spearman’s rho are: the uniformity index for each of the tree families between the two study sites, the model residues for each of the families and the three parameters to estimate from the model. The cor.test function in the R [@R2018] statistical programming environment was used to calculate Spearman’s rho. We used a 95 percent confidence interval.

>>>>

## Sampling
The dataset used in this study came from genetic selection for a series of tests according to provenances [@Beaulieu1996]. The improvement program for this region was led by Quebec’s Ministry of Forests, Wildlife and Parcs, Canada. Experimental plantings were initiated from white spruce seedlings grown in nurseries and planted at two years of age at a regular spacing between trees of 2 m in all directions. This series of tests was established in 1999 by the Canadian Forest Service and is one of the three essential parts of the white spruce breeding program in Quebec. Two sites were selected for sampling: one near Saint-Casimir, Quebec (46.6994, -72.1119), in the maple–basswood ecological zone (warm weather) , and the other one near Cabano (Asselin), Quebec (47.8808, -68.4436), in the balsam fir-yellow birch ecological zone (cool weather) (fig 1). Between 9 and 14 trees per site were sampled from each of the 93 full-sib families, for a total sample of 2365 trees. Tree height and diameter at breast height (DBH, 1.3 m above ground) were recorded in 2015 at the age of 15 years, and a wood increment core was extracted from the south facing side of each tree. Cores were stored in a freezer, conditioned to 7% moisture and cut to 1.68 mm thickness prior to X-ray densitometry analyses (Quintek Measurement Systems, TN). Wood density was calculated as a ring area weighted mean from recorded pith to bark wood density profiles.

@@

where RD is the mean ring density (kg.m^-3^), CA is cambial age (years), $b_0$, $b_1$ and $b_2$ are empirically determined parameters, and e is the residual error term. Parameter $b_0$ denotes the intercept when CA approaches a theoretical value of 0. We noticed that it was impossible to optimize the equation using the same estimated parameters for all tree cores, because the pattern of variation of annual rings average density of each tree is more or less different from the others. We, therefore, used the optim function of the stats package in the R [@R2018] statistical programming environment to find the best parameters iteratively for each tree core . The fit of the model was evaluated by visual analysis of the model residual curves against adjusted values and explanatory variables, fit indices (R^2^) [@Pape1999]. The graphic description in figure 2 of the three parameters of our model makes it possible to understand how each parameter influences our model (Fig 2).

@@

It can be observed in figure 2 that the parameters $b_0$ and $b_1$ influence the whole of the curve. An increase of one of these parameters leads to that of the density on all rings. Unlike parameter $b_0$ and $b_1$, parameter $b_2$ seems to be influenced by some of the density. A low value of this parameter causes a sharp increase of the density starting from the third ring and when this parameter increases a decrease of the density is observed at this level until the curve is similar to the cases of the parameters $b_0$ and $b_1$. Beyond the value 1, the parameter $b_2$ does not influence the variation of the density.\

## Determination of the wood density variability index
The variability index is an index to determine the variation in the density of pith-to-bark in order to identify tree families that are least sensitive to variations in climatic conditions. The residues of our model were used to obtain the wood density variability index, which was determined using an equation. We subtracted the density residues values of year $n-1$ from year $n$. We were interested more specifically in the difference between the average density residues of annual rings of two consecutive years, no matter whether the difference was positive or negative. The absolute value was used for each difference to get rid of the sign. The index was estimated from the following formula:

$$V = \sum | D_n - D_{n - 1} |$$

Where V is the variability index, $D_n$ is the wood density residues of year $n$ and  $D_{n - 1}$ is the tree density residues of year $n-1$.

## Spearman’s rank correlation coefficient (Spearman’s rho) 
To describe the link between two variables by means of a monotonic function, we used Spearman’s rank correlation coefficient. We calculated this coefficient for the index of variability and the different parameters of the model. The elements for which we calculated Spearman’s rho are: the variability index for each of the tree families between two study sites, the model residues for each of the families and the three parameters to estimate from the model. The cor.test function in the R [@R2018] statistical programming environment was used to calculate Spearman’s rho. We used a 95 percent confidence interval.
